Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-07 documentation/paper.tex
Reorganization and clarification of purpose of supervised learning

In this study, newly developed methodologies were compared to the following discrimination techniques developed previously for the PICO-60 experiment.

@@

Two semi-supervised algorithms were developed and implemented for this study: gravitational differentiation and iterative cluster nucleation. Both are discussed in detail in section \ref{semi_supervised}.

\subsection{Hyperparameter Optimization}

Learning algorithms in this study are optimized using grid searches, in which many different combinations of hyperparameters are tested. The computational work required for a grid search increases exponentially with the number of hyperparameters $n$ and the number of options per hyperparameter $m$; to be exact, its complexity is $O(m^{n})$. Thus, it is important to minimize the number of hyperparameters that are optimized at once.

Since the semi-supervised learning algorithms used incorporate neural network models, optimization is a much simpler task if the network's hyperparameters are already optimized. Thus, the optimization task is split into two distinct phases:

\begin{enumerate}
    \item Optimize the hyperparameters of a neural network on validation accuracy, to accurately reproduce the imperfect ground truths it is trained on. While this does not produce an optimal discriminator, it does reveal architectures that are capable, in essence, of learning to accomplish the discrimination task.
    \item Using neural network hyperparameters that were determined to be effective, optimize the hyperparameters of the semi-supervised learning algorithm to reproduce Acoustic Parameter as closely as possible. Since Acoustic Parameter is not used to optimize the neural network directly at any point, models that excel at this task demonstrate an ability to learn the desired discriminator while ignoring the impurities in the training set.
\end{enumerate}

@@

Supervised learning was the first general technique that was applied and optimized. It makes use of fully (but imperfectly) labeled calibration data sets, which are used for training. Performance of these supervised neural networks is evaluated based on its accuracy at replication of the provided labels on a validation set (which is set aside and not trained on).

@@

@@

@@

@@

@@

Iterative cluster nucleation is a semi-supervised learning algorithm that takes advantage of some amount of imperfectly labeled data, using it to classify the rest of an unlabeled training set while optimizing to produce an effective discriminator. The algorithm is initialized as follows:

>>>>

\subsubsection{Overview}

In this study, newly developed methodologies were compared to the 2 discrimination techniques developed previously for the PICO-60 experiment: Acoustic Parameter and machine learning.

@@

2 semi-supervised algorithms were developed and implemented for this study: gravitational differentiation and iterative cluster nucleation. Both are discussed in detail in section \ref{semi_supervised}.

\subsection{Optimization Process}

Learning algorithms in this study are optimized systematically, with a variety of neural network configurations and input formats. To obtain meaningful results, it is important to minimize the number of variables during each individual run. Thus, since the 2 semi-supervised algorithms incorporate neural network models, it is important that the input formats and other hyperparameters of these networks are optimized first to some degree. This means the task is split into 2 distinct phases:

\begin{enumerate}
    \item Develop and verify several different supervised learning systems. Their performance is evaluated based on their ability to replicate the ground truths they are trained on. While this does not produce an optimal discriminator, it does reveal architectures that are capable, in essence, of learning to accomplish the discrimination task.
    \item Using general supervised learning systems and input formats that were determined to be effective, optimize the hyperparameters of the semi-supervised learning algorithm to reproduce Acoustic Parameter as closely as possible. Since Acoustic Parameter is not used to optimize the neural network directly at any point, models that excel at this task demonstrate an ability to learn the desired discriminator while ignoring the impurities in the training set.
\end{enumerate}

@@

\subsection{Overview}

Important unknowns to be determined through experimentation with supervised learning included the most effective input format for the network, and the associated general network structure. Three major such configurations were applied:

\begin{enumerate}
    \item A convolutional neural network trained on the raw waveform $\omega$.
    \item A dense neural network trained on banded Fourier transforms $\beta_{N}$.
    \item A convolutional neural network trained on the image window data $\iota$.
\end{enumerate}

In addition, configurations with and without application of $WallCut(D)$ were tested. While $WallCut(D)$ was used throughout the original PICO-60 analysis because it is necessary for Acoustic Parameter, it was unknown whether or not it was required for neural networks.

@@

\subsubsection{Structure}

@@

\subsubsection{Results}

@@

\subsection{Overview}

@@

\subsubsection{Concept}

@@

\subsubsection{Concept}

Iterative cluster nucleation is a semi-supervised learning algorithm that takes advantage of some amount of imperfectly labeled data, using it to classify the rest of an unlabeled training set while optimizing to produce an effective discriminator.

\subsubsection{Structure}

The algorithm is initialized as follows:
